%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

% of this license or (at your option) any later version.
% The latest version of this license is in http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
%
% This work has the LPPL maintenance status `maintained'.
% 
% The Current Maintainer of this work is Simon Thelin.
%
% This work consists of the files main.tex

\documentclass[11pt,a4paper,sans]{moderncv}       

 % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}

\usepackage[utf8]{inputenc}   
\usepackage{changepage}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{changepage}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage[multiple]{footmisc}
\usepackage[T1]{fontenc}


\newlength{\mylen}
\setbox1=\hbox{$\bullet$}\setbox2=\hbox{\tiny$\bullet$}
\setlength{\mylen}{\dimexpr0.5\ht1-0.5\ht2}

\usepackage[scale=0.90]{geometry}

\address{Fruktträdsgatan 11, 417 19}{Göteborg, Sweden}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provid0731-560387ed empty
\phone[mobile]{+4670~986~53~92}                   %                   % optional, remove / comment the line if not wanted
\email{simon.thelin90@gmail.com}    


\name{Simon}{Thelin}

\pagestyle{fancy}
\fancyhf{}
\lhead{\nouppercase{\rightmark} (\nouppercase{\leftmark})}
\rhead{}
\lhead{}
\rfoot{}
\lfoot{}

\begin{document}

%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\setlength{\parskip}{0.25em}
\vspace{-35.0pt}
%\section{Objective}
%I strive to work in a fast changing and challenging working environment where i can use and increase my skills. I possess a wide knowledge in fleet management systems that could help to improve available products and let me grow with the company and drive the business into success.

%\section{Qualification highlights}
%I possess professional qualifications in programming where i have delivered applications both in Android and hardware close software. I am always on point and loyal towards my duties.
\section{Work Experience}

\cventry{January 2018 -- (ongoing) }{Developer Connected Vehicle Cloud}{Ericsson AB}{Gothenburg}{}{
\begin{itemize}
    \itemsep0.3em
    \item Developer for Continuous Deployment (CD), KeyCloak, Microservices, Kafka, Java Spring, Terraform, Elastic Search, Kibana and Ansible.
\end{itemize} 
}

\cventry{June 2017 -- December 2017 }{Software Engineer}{Drivec AB}{Helsingborg}{}{
\begin{itemize}
    \itemsep0.3em
    \item Integrating GPRS/GPS and CAN\footnotemark[1] hardware. Preparing data for machine learning solutions. Quality assurance work involving analyzing data from vehicles. Technology's used such as Node.js, Android.
\end{itemize} 
}

\cventry{June 2011 -- May 2017 }{Support \& Field Test Engineer}{Drivec AB}{Helsingborg}{}{
\begin{itemize}
    \itemsep0.3em
    %\item Project launches, installations, installation manuals, vehicle configuration.
    \item Technical and customer support together with calibration of fleet management systems across 3000 vehicles to clients and customers in the Nordic region.
    \item Responsible for project roll outs of vehicles in the Nordic region.
    \item Performed reverse engineering on vehicle data protocols\footnotemark[1].
    %\item CAN-bus data analysis, reverse engineering.
\end{itemize} 
}

\cventry{June 2015 -- March 2017
}{Software Engineering Trainee }{Drivec AB}{Helsingborg}{}{
\begin{itemize}
    \itemsep0.3em
    %\item Science Research - ECO-driving.
    %\item Android development - GUI, TCP/IP.
    \item Responsible for the user interface and backend communication layer for an eco-driving Android application.
    %\item Field tests including research and analysis of data protocols\addtocounter{footnote}{-1}\footnotemark{} on tractor and harbour trucks where the results were implemented in the Android application.
\end{itemize}}

\cventry{March 2016 -- May 2016 
}{Algorithm \& Data Structure T.A}{Halmstad University}{Halmstad}{}{
\begin{itemize}
    \itemsep0.3em
    \item Teaching assistant during computer labs in the Data Structure and Algorithms in Java course.
\end{itemize}}

\section{Education}
\cventry{2014--2017}{Computer Science \& Engineering}{Halmstad University}{Sweden}{}{ \begin{itemize}
    \itemsep0.3em
    \item \textit{\textbf{Delivered a cloud module called ITMS\footnotemark[2] - Machine learning approach}}. Which was honored as the best thesis in the categories of Computer Science, Electronic, Mechatronic Engineering.
    \item Delivered a prototype for an ingredient check up app for allergy at the hackathon Hack4Health in April 2016.
    \item Attended education and preparations for 6 months to be able to be responsible for the team building process for new students at the introduction week at the IT section fall 2015.
    \item Representative during the open day in March 2017 for the IT section at Halmstad University.
\end{itemize}}{ }

\cventry{2016--2017}{Exchange Student BA Computer Science \& Engineering}{Korea University}{South Korea}{87.2/100 GPA}{
\begin{itemize}
    \itemsep0.3em
    \item Attended courses in Computer networks, Information security,  Software Engineering, Internet Programming together with international and Korean students.
    \item Developer for the anonymous location based messages application \href{www.klotter.co}{\textbf{\textsc{www.klotter.co}}} together with international students, A+ received.
\end{itemize}}{}  % arguments 3 to 6 can be left empty

\cventry{2012--2013}{Computer Science}{Malmö University}{Sweden}{}{}{}  % arguments 3 to 6 can be left empty

\section{Language skills}
Native Swedish speaker, fluent in English and beginner knowledge of Korean.
\section{Technical skills - Practical Experience}
{Programming/Script language\footnotemark[3]:  \textbf{\textit{Java$\rightarrow 3$, C$\rightarrow 3$, Javascript$\rightarrow 3$, Python$\rightarrow 3$}} \textbf{\textit{Terraform$\rightarrow 2$, Ansible$\rightarrow 1$}}}\\
{Applications\footnotemark[3]:
\textbf{Microsoft Office$\rightarrow 3$, Libre Office$\rightarrow 3$, Mathematic$\rightarrow 2$, MatLab/Octave$\rightarrow 2$, Eclipse$\rightarrow 3$, IAR Studio$\rightarrow 2$, Visual Studio Code$\rightarrow 2$, IntelliJ IDE's$\rightarrow 3$, \textit{shareLaTeX$\rightarrow 3$}, Git$\rightarrow 2$, Gerri$\rightarrow 2$}

\section{References}
    \href{https://github.com/Thelin90}{\textbf{\textsc{[GitHub]}}}
     \href{https://www.linkedin.com/in/simon-thelin-3ba96986/}{\textbf{\textsc{[LinkedIn]}}}
     \href{http://hh.diva-portal.org/smash/record.jsf?pid=diva2%3A1113511&dswid=4291#sthash.wwKv4JYI.dpbs}{\textbf{\textsc{[Thesis: ITMS\footnotemark[2] - Machine Learning Approach]}}}
     \href{http://iopscience.iop.org/article/10.1088/1757-899X/252/1/012018/pdf;jsessionid=EF9A9E415EC41D639019919DC566B21F.c4.iopscience.cld.iop.org}{\textbf{[IOP Science Publication: ITMS\footnotemark[2] - Machine Learning Approach]}}
     
\vfill
\enlargethispage{\footskip}
\footnotetext[1]{CAN - Controller Area Network}
\footnotetext[2]{ITMS - Indirect Tire Monitoring System}
\footnotetext[3]{Level 1 = beginner, 2 = basic, 3 = intermediate , 4 = advanced}

\end{document}


%% end of file `template.tex'.
