%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

% of this license or (at your option) any later version.
% The latest version of this license is in http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
%
% This work has the LPPL maintenance status `maintained'.
% 
% The Current Maintainer of this work is Simon Thelin.
%
% This work consists of the files main.tex

\documentclass[10pt,a4paper,sans,colorlinks,linkcolor=blue,urlcolor=blue]{moderncv}       

 % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}    
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}

\usepackage[utf8]{inputenc}   
\usepackage{lmodern}
\usepackage{changepage}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{changepage}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage[multiple]{footmisc}
\usepackage[T1]{fontenc}




\newlength{\mylen}
\setbox1=\hbox{$\bullet$}\setbox2=\hbox{\tiny$\bullet$}
\setlength{\mylen}{\dimexpr0.5\ht1-0.5\ht2}

\usepackage[scale=0.9]{geometry}

\address{Flat 33, Canada Wharf, 255, Rotherhithe Street, London, SE16 5ES, UK}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provid0731-560387ed empty
\phone[mobile]{(+44)~07544~38~23~09}                   %                   % optional, remove / comment the line if not wanted
\email{simon.thelin90@gmail.com}

\extrainfo{\homepagesymbol\httplink{www.linkedin.com/in/simon-thelin-3ba96986/}}

\name{Simon}{Thelin}

\pagestyle{fancy}
\fancyhf{}
\lhead{\nouppercase{\rightmark} (\nouppercase{\leftmark})}
\rhead{}
\lhead{}
\rfoot{}
\lfoot{}

\begin{document}

\textbf{Lead Data Engineer - DataOps Fundamentalist}

%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\setlength{\parskip}{0.045em}
\vspace{-30.0pt}

\section{Work Experience}

\cventry{Current - May 2022}{Lead Data Engineer}{7bridges}{London, UK}{\textbf{full time}}{
\begin{itemize}
    \itemsep0.2em
    \item Leading efforts in end to end implementation of 7Bridges data platform, pushing it to the next level for analytics, AI and beyond.
    \item Reducing compute and storage costs over 100\%.
    \item Reducing query latency up to 100\%.
    \item Introducing new ways of learning and pushing efforts in hackathons to push innovation.
    \item Documented improvement of output of team members delivering projects 1-2 quarters faster than normal.
    \item Introducing DataOps workflows. 
    \item Main focus on Lakehouse architecture for batch, streaming. Inspired but not exclusive to datamesh. 
    \item Huge focus on self serve around data. Built on top of open source technologies such as delta, mlflow, spark on k8s, kafka, trino, dbt, airbyte.
\end{itemize} 
}

\cventry{Dec 2021 - May 2022}{Lead Data Engineer}{Kainos}{London, UK}{\textbf{Full Time Consultant}}{
\begin{itemize}
    \itemsep0.2em
    \item Working on architecture and guidance to current data platforms on consultant basis.
\end{itemize} 
}

\cventry{Aug 2020 - Dec 2021}{Data Engineer}{IMG Arena}{London}{\textbf{full time}}{
\begin{itemize}
    \itemsep0.2em
    \item Designed Lakehouse architecture based on Apache Druid, data processing pipelines both streaming and batch.
    %\item Contributed to feature engineering, combining data sets from internal and external sources.
    \item Managed and maintained standards for Data Analysis tools used across the organisation.
    %\item Implemented the full life cycle of machine learning models.
    \item Engaging with sports data providers about source data quality.
    \item Contributing to future design/architecture solutions that directly impact the business.
\end{itemize} 
}

\cventry{Dec 2019 - June 2020}{Data Engineer}{GameAnalytics}{London}{\textbf{full time}}{
\begin{itemize}
    \itemsep0.2em
    \item Improved current data pipeline built in PySpark and Hive to insert data into BigQuery.
    \item Built up the company data science platform. Including being responsible for best practices for data engineering and implementing data science features.
    \item Introduced Apache Airflow from scratch. Responsible for maintaining, teaching others (workshops) in how our schedule and workflow platform works in the data team, and how it can be used elsewhere.
    \item Worked closely together with data scientist to put statistical AB testing models into production. This included both data engineering and data science aspects.
\end{itemize} 
}

\cventry{Dec 2019 - June 2019}{Data Engineer}{YoYo Wallet}{London}{\textbf{full time}}{
\begin{itemize}
    \itemsep0.2em
    \item Engineered large scale data modeling. Data processing in real time and batch with analytics. 
    %\item Used technologies such as Apache Spark, Terraform, Kafka, AWS (Redshift, S3, ECS, Kinesis), Postgres, Python, Pandas, Faust, Alembic, ELK stack, Airflow.
    \item Managed the transitioning of the data warehouse from Postgres to utilise Redshift.
    %\item Managing an intern within the data team.
\end{itemize} 
}

\cventry{Aug 2018 - June 2019}{Data Engineer}{Yieldify}{London}{\textbf{full time}}{
\begin{itemize}
    \itemsep0.2em
    %\item Engineered large scale data modeling. Batch processing and analytics.
    \item Maintaining maintenance of Redshift with Alembic.
    \item Working closely with Data Analysts to deliver business needs both ad-hoc and modifying existing architecture. 
\end{itemize}}

\cventry{August 2018 - Jan 2018}{Developer Connected Vehicle Cloud}{Ericsson AB}{Gothenburg, Sweden}{\textbf{full time}}{
\begin{itemize}
    \itemsep0.2em
    \item Worked closely towards OEMs and OEMs delivery partners. Developing connectivity for the modern automotive ecosystem.
    %\item Worked on maintaining Kafka infrastructure.
    \item Engineered micro-service infrastructure in Ericcsons cloud environment based on Apcera (similar to k8s).
    %\item Collaborating with several teams in China with code reviews.
    %\item Utilising Terraform to enforce infrastructure as code in multi cloud environments (Azure, AWS).
\end{itemize}}

\cventry{Dec 2017- June 2017}{Software Engineer}{Drivec AB}{Helsingborg, Sweden}{\textbf{full time}}{
\begin{itemize}
    \itemsep0.2em
    \item Performed analytical work against fleet management systems. Integration of GPRS/GPS and CAN hardware. Preparing data for machine learning solutions, such as using Hellinger Distance.
    %\item Quality assurance work involving analyzing data from vehicles.
    %\item Used technologies such as Python, Node.js and Android (Java).
\end{itemize}}

\cventry{2011 June - 2014 Sep}{Support \& Field Test Engineer}{Drivec AB}{Helsingborg, Sweden}{\textbf{full time}}{\begin{itemize}
    %\itemsep0.2em
    %\item Worked in the company to make sure the project role out, managing installations went smoothly. Included traveling around the Nordics to teach how to install the fleet management systems.
    \item Analyze CAN-bus data from vehicles. % to find bugs in the system.
   % \item Handled customer relationships with both small and big businesses.
\end{itemize}}

\newpage
\section{Education}
\cventry{2014 - 2017}{BA of Science in Engineering, Computer Science \& Engineering}{Halmstad University}{Sweden}{}{ \begin{itemize}
    \itemsep0.2em
    \item \textit{\textbf{Machine Learning thesis project where we delivered a cloud module called ITMS - MLA\footnotemark[2]}}. Which was honored as the best thesis in the categories of Computer Science, Electronic, Mechatronic Engineering.
    \item Delivered a prototype for an ingredient check up app for allergy at the hackathon Hack4Health in April 2016.
    \item Attended education and preparations for 6 months to be able to be responsible for the team building process for new students at the introduction week at the IT section fall 2015.
    \item Representative during the open day in March 2017 for the IT section at Halmstad University.
\end{itemize}}{ }

\cventry{2016 - 2017}{Exchange Student BA Computer Science \& Engineering}{Korea University}{KOR}{87.2/100 GPA}{
\begin{itemize}
    \itemsep0.3em
    \item Attended courses in Computer networks, Information security,  Software Engineering, Internet Programming together with international and Korean students.
    \item Developer for the anonymous location based messages application \href{www.klotter.co}{\textbf{\textsc{www.klotter.co}}} together with international students, A+ received.
\end{itemize} 
} % arguments 3 to 6 can be left empty

\cventry{2012 - 2013}{Computer Science}{Malmö University}{Sweden}{}{}{}  % arguments 3 to 6 can be left empty

\section{Leadership skills}
\begin{itemize}
\item Leading small teams on large projects through mentor ship and guidance to solve complex business problems.
\item Aligning with other squads/teams teaching new technologies.
\item Taking on product management duties to deliver end to end data products.
\item Pushing team members and companies to learn new areas of work such as infrastructure as code, end to end architecture sessions, understanding the importance of having skills across the board to deliver successful data projects.
\end{itemize}

\section{Technical skills}

\begin{itemize}
    \item Programming:\textbf{\textit{\textasciitilde6 years: Python, \textasciitilde1 year: Scala}}
    \item SQL Syntax:\textbf{\textit{Various engines from Postgres to Trino to Druid, whatever it is, hands on it.}}
    \item Infrastructure As Code:\textbf{\textit{\textasciitilde3 years: Terraform}}
    \item Job Scheduler Platform:\textbf{\textit{\textasciitilde4 years: Apache Airflow, \textasciitilde3 years: Native K8S, \textasciitilde1 years: Argo Workflow, \textasciitilde2 years: AWS Serverless}}
    \item BI Tools:\textbf{\textit{\textasciitilde2 years: Apache Superset, \textasciitilde2 years: Metabase, \textasciitilde1 years: Tableau}}
    \item Distributed Computing:\textbf{\textit{\textasciitilde1 year: Scala Spark, \textasciitilde4 years: PySpark, \textasciitilde1 years: Hive}}
    \item Parallel Computing: 
    \textbf{\textit{\textasciitilde3 years: Pandas}}
    \item Stream Processing: \textbf{\textit{(\textasciitilde3 years: Apache Kafka)}}
    \item CI: \textbf{\textit{\textasciitilde3 years: Jenkins , Travis, CircleCI, GitLab}}
    \item CD: \textbf{\textit{(>4 years: Docker, Docker-Compose), >3 years: ArgoCD)}}
    \item Main DB Technologies:\textbf{\textit{(Columnar: Trino, Druid, Redshift, BigQuery, Athena), (NoSQL: DynamoDB), (RDBMS: Postgres, MySQL)}}
    \item Main Cloud Technology:\textbf{\textit{(>5 years: AWS), (<1 year: Google Cloud)}}
    \item Certifications:\href{https://www.coursera.org/account/accomplishments/certificate/W5HM63ABYCDV}{\textbf{\textsc{\underline{[Coursera - Machine Learning]}}}}
    \item Publications ITMS - MLA\footnotemark[2]: \href{http://hh.diva-portal.org/smash/record.jsf?pid=diva2%3A1113511&dswid=4291#sthash.wwKv4JYI.dpbs}{\textbf{\textsc{\underline{[Thesis - Diva Portal]}}}}\href{http://iopscience.iop.org/article/10.1088/1757-899X/252/1/012018/pdf;jsessionid=EF9A9E415EC41D639019919DC566B21F.c4.iopscience.cld.iop.org}{\textbf{\underline{[IOP Science Publication]}}}
\end{itemize}

\section{References}
Conference Speech Of Lakehouse Architecture:\underline{\href{https://www.starburst.io/datanova/on-demand/?wvideo=n53ubhz7hb}{\textbf{\textsc{[DataNova 2023]}}}}\\
Portfolio: \underline{\href{https://github.com/Thelin90}{\textbf{\textsc{[GitHub]}}}}\\
Honors \& Awards: \href{https://www.hms-networks.com/work/in/sweden/hms-scholarship}{\textbf{\underline{[Scholarship - Best Thesis]}}} \href{http://www.hh.se/omhogskolan/aktuellt/nyheter/nyheter/studenterbelonasavsparbanksstiftelsenkronan.65446700.html}{\textbf{\underline{[Scholarship - Sparbanken Kronan]}}}

\vfill
\enlargethispage{\footskip}
\footnotetext[1]{CAN - Controller Area Network}
\footnotetext[2]{ITMS MLA - Indirect Tire Monitoring System - Machine Learning Approach}
\end{document}


%% end of file `template.tex'.
